---
title: "Lab Review 3"
author: "Hoang Nguyen"
date: "Feb 17, 2017"
output: 
    revealjs::revealjs_presentation:
        theme: sky
        highlight: pygments
        center: true
        transition: concave
        self_contained: false
        reveal_plugins: ["notes", "search","zoom","chalkboard"]
        reveal_options:
            chalkboard: 
                theme: chalkboard
                toggleNotesButton: true
            menu:
                numbers: true
---

# New words

# **Deterministic process** vs **stochastic process** 

----

$$Y_t = \{y_1, \ldots, y_T \}$$
    
<small> See an example that [Daniel McLaury](https://www.quora.com/What-are-stochastic-and-deterministic-processes-And-how-can-I-learn-more-about-these) gives </small>

----

- A deterministic process is one where the present state completely determines the future state.  If I make a (riskless) investment of \$1,000 at 5\% interest, compounded annually, then in one year's time I will have \$1,050, in two years' time I will have \$1,102.50, and so forth.

> - A stochastic process, on the other hand, is one where there's some randomness or uncertainty involved.  If I buy \$1,000 worth of IBM stock today, how much money will it be worth in one year's time?  In two years' time?  Who knows?  This is a stochastic process. 

----

Another example of the Monthly U.S. airline passenger-miles: 01/1996 - 05/2005.

```{r error=FALSE, warning=FALSE,echo=FALSE, message=FALSE}
library(TSA)
data(airmiles) # Monthly U.S. airline passenger-miles: 01/1996 - 05/2005.
plot(airmiles)
```

# **Means, Variances, and Covariances**

----

mean function

$$ \mu_t = E(Y_t) = \sum_{i = 1}^T y_i /T$$

----

autocovariance function

$$
\begin{split}
\gamma_{t,s} & = Cov(Y_t, Y_s) \\
& = E((Y_t - \mu_t)(Y_s - \mu_s)) \\
& = E(Y_t Y_s) - \mu_t \mu_s
\end{split}
$$

----

autocorrelation function

$$ 
\begin{split}
\rho_{t,s} & = \frac{ Cov(Y_t, Y_s)}{\sqrt{ Var(Y_t) Var(Y_s)}} \\
& = \frac{\gamma_{t,s}}{\sqrt{\gamma_{t,t} \gamma_{s,s}}}
\end{split}
$$

The properties of $\rho_{t,s}$? range?

# **Random Walk**

----

```{r error=FALSE, warning=FALSE,echo=FALSE, message=FALSE}
data(rwalk) # rwalk contains a simulated random walk
plot(rwalk,type='o',ylab='Random Walk')
```

----

Let $e_1 , e_2 ,...$ be a sequence of independent, identically distributed random variables each with zero mean and variance $\sigma_{e}^2$. 

$$
\begin{aligned}
Y_1 &= e_1 \\
Y_2 &= Y_1 + e_2 \\
...& \\
Y_t &= Y_{t-1} + e_t \\
\end{aligned}
$$

Properties of random walk?
[Mean and Variance](https://www.youtube.com/watch?v=b2IImYrf-pQ)

# **Stationarity**

----

A random process ${X(t),t \in T}$ is stationary if its statistical properties do not change by time.

> - Strict-sense stationary means joint CDF of $X(t_1), X(t_2) , ... , X(t_r)$ is equal to $X(t_1 + \Delta), X(t_2 + \Delta) , ... , X(t_r + \Delta)$ 
> - Weak-sense stationary means 
$$
\begin{aligned}
E[X(t_1)] &= E[X(t_2)] \\
E[X(t_1)X(t_2)] &= E[X(t_1+\Delta)X(t_2+\Delta)]
\end{aligned}
$$

----

Random walk is stationary?


```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
eps = rnorm(10000)
randomwalk = cumsum(eps)
plot(randomwalk, type = "l")
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
acf(randomwalk)
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
pacf(randomwalk)
```

----

## White Noise

[Wiki on White Noise](https://en.wikipedia.org/wiki/White_noise)
```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
plot(eps, type = "l")
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
acf(eps)
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
pacf(eps)
```

# **Trend Stationary** vs **Difference Stationary**

----

You can write a **trend-stationary** process, $y_t$, as

$$y_t= \mu_t+\epsilon_t$$

where:

-    $\mu_t$ is a deterministic mean trend.

-    $\epsilon_t$ is a stationary stochastic process with mean zero.

----

You can write a **difference stationary** process, $y_t$, as

$$ \Delta^D y_t= \mu + \epsilon_t$$

where:

-   D is D th-degree differencing operator.

-    $\mu$ is a constant.

-    $\epsilon_t$ is a stationary stochastic process with mean zero.

----

Make your guess? 

**Trend Stationary** or **Difference Stationary**

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5, echo=FALSE}
data(ar1.2.s)
ar1.s = ar1.2.s
trend_stationary = time(ar1.s) * 0.1 + ar1.s
diff_stationary = cumsum(ar1.s)
plot(trend_stationary, type = "l" , lwd = 2, col = "red", ylim = c(-10,20), ylab = "")
lines(diff_stationary, col = "blue")
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
acf(trend_stationary)
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
pacf(trend_stationary)
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
acf(diff_stationary)
```

----

```{r error=FALSE, warning=FALSE, message=FALSE, fig.height= 5}
pacf(diff_stationary)
```

